---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ucminf

<!-- badges: start -->
[![R-CMD-check](https://github.com/hdakpo/ucminf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hdakpo/ucminf/actions/workflows/R-CMD-check.yaml)
[![Downloads](https://cranlogs.r-pkg.org/badges/ucminf)](https://CRAN.R-project.org/package=ucminf)
[![](https://img.shields.io/github/languages/code-size/hdakpo/ucminf.svg)](https://github.com/hdakpo/ucminf)
[![](https://img.shields.io/badge/license-GPL-blue)](https://github.com/hdakpo/ucminf)
[![CRAN status](https://www.r-pkg.org/badges/version/ucminf)](https://CRAN.R-project.org/package=ucminf)
<!-- badges: end -->

The goal of *ucminf* is to provide an algorithm for general-purpose 
unconstrained non-linear optimization. The algorithm is of quasi-Newton type 
with BFGS updating of the inverse Hessian and soft line search with a trust 
region type monitoring of the input to the line search algorithm. The interface 
of *ucminf* is designed for easy interchange with `optim`

## Installation

You can install the development version of ucminf from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hdakpo/ucminf")
```

## Example

```{r example}
library(ucminf)
# Rosenbrock Banana function
fR <- function(x) (1 - x[1])^2 + 100 * (x[2] - x[1]^2)^2
gR <- function(x) c(-400 * x[1] * (x[2] - x[1] * x[1]) - 2 * (1 - x[1]),
                     200 * (x[2] - x[1] * x[1]))
##  Find minimum and show trace
optRes <- ucminf(par = c(2,.5), fn = fR, gr = gR, control = list(trace = 1))
```
